---
title: "p8105_hw1_ltc2121"
output: github_document
---

```{r, echo = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  fig.width = 6,
  fig.asp = .6,
  out.width = "90%"
)
library(tidyverse)
```

# Problem 1 

## Importing Data

```{r}
data("penguins", package = "palmerpenguins")
```

The penguins dataset has `r nrow(penguins)` rows and `r ncol(penguins)` columns. The variables in the dataset are `r names(penguins)`. The mean flipper length is `r mean(penguins$flipper_length_mm, na.rm = TRUE)` mm. The frequency among the different species of penguins in the data is `r table(penguins$species)`. The frequency among the different islands in the data is `r table(penguins$island)`. The frequency between female and male in the dataset is `r table(penguins$sex)` respectively. 

## Penguin Plot

```{r}
plot_penguin = 
  ggplot(penguins, 
       aes(x = bill_length_mm, y = flipper_length_mm, color = species)) +
  geom_point()
plot_penguin

ggsave("penguin_scatterplot.png", plot = plot_penguin)
```

# Problem 2

## Making a Data Frame 

```{r}
hw_data = 
  tibble(
    vec_num = rnorm(10), 
    vec_log = (vec_num > 0), 
    vec_char = c("this", "is", "hw1", "data", "here", "that", "we", "need", "for", "class"), 
    vec_fac = factor(c("low", "mid", "high", "low", "mid", "high", "low", "mid", "high", "low"))
  )
```

## Mean of Variables 

The mean can be derived from of the numbered vector and logical vector. The character vector and factor vector result in an "NA" mean value. 

```{r}
hw_data %>% 
  pull(vec_num) %>% 
  mean()

hw_data %>% 
  pull(vec_log) %>% 
  mean()

hw_data %>% 
  pull(vec_char) %>% 
  mean()

hw_data %>% 
  pull(vec_fac) %>% 
  mean()
```

## Change Variable Type 

When the character is converted to numeric the string of characters is not recognized as another pattern and all values for the vector become "Na". This corresponds with the result previously received when attempting to take the mean of the character vector. 

The logical variables have an integer vector associated with their constants. This is recognized as TRUE = 1 and FALSE = 0 which are the values assigned to the variable once it is converted to a numeric. This integer value is known in R which is why the mean of the logical variable resulted in an integer. 

The factor variable does not have an integer innately associated with the factor levels and resulted in an mean of "NA". When the factor is converted to a numeric, it is assigned a integer number that corresponds to the factor level. 

```{r eval=FALSE}
hw_data$vec_fac <- as.numeric(hw_data$vec_fac)

hw_data$vec_char<- as.numeric(hw_data$vec_char)

hw_data$vec_log <- as.numeric(hw_data$vec_log)
```

